Bayesian MCMC diagnostics and summarisation using Tracer 1.6

### 2017-08-01 manuscript/tracer16.tex
abstract

\section{Motivation:}
%Computational evolutionary biology, statistical phylogenetics and coalescent-based population genetics are becoming increasingly central to the analysis and understanding of molecular sequence data. 
Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) plays a central role for understanding the story of evolutions from molecular sequence data.  
The comprehension of posterior distributions from an implementation of this framework is the significant matter.
\section{Results:}
%We describe here a software package, Tracer version 1.6, which ... 
We here present a software package \emph{Tracer} (version 1.6) for visualising and analysing the trace files generated by Bayesian MCMC runs. 
It also provides kernel density estimation, cheap marginal likelihood estimator, 
multivariate analyses (is this reluctant?), %TODO
demographic trajectory reconstruction, conditional posterior distribution summary, etc. 
\section{Availability:}
Tracer is open-source under the GNU lesser general public license and available at 
\url{http://beast.bio.ed.ac.uk/Tracer} and \url{https://github.com/beast-dev/tracer}.

>>>>

\section{Motivation:}
%Computational evolutionary biology, statistical phylogenetics and coalescent-based population genetics are becoming increasingly central to the analysis and understanding of molecular sequence data. 
Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) plays a central role in understanding evolutionary history and processes from molecular sequence data.  
Visualising and analysing the samples from the posterior distribution is a key step in any non-trivial Bayesian inference, and it is especially important for methods that employ MCMC.
\section{Results:}
Here we present a software package \emph{Tracer} (version 1.6) for visualising and analysing the trace files generated by Bayesian MCMC runs. 
The \emph{Tracer} software also provides kernel density estimation, cheap marginal likelihood estimation, 
multivariate visualisation, demographic trajectory reconstruction, conditional posterior distribution summary and more. 
\section{Availability:}
Tracer is open-source under the GNU lesser general public license and available at 
\url{http://beast.bio.ed.ac.uk/Tracer} and \url{https://github.com/beast-dev/tracer}.
